Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-12 article/article.Rmd
Commit 2024-06-12 11:11

The distribution of the number of CE events as a function of OIR is shown in
Figure\nobreakspace{}\ref{fig:ovir-distribution}. Apparently, there is an inverse
relation between the frequency of CE events  and OIR with an exponential-like
decline. This is expected, as the stronger the CE events become, the rarer are the
conditions favoring the occurrence of CE events. For the majority (over $62\%$) of
the CE events the OIR is below the long term average of
$`r round(mean(ST_E_yearly$GLB_diff.mean), 1)`\,\text{W}/\text{m}^2$,
while about $8.1\%$ of the events correspond to OIR larger than
$100\,\text{W}/\text{m}^2$ and up to highest value of $412.4\,\text{W}/\text{m}^2$.
This distribution is indicative of the magnitude and the probability of the expected
CE events over Thessaloniki.  Similar distribution of CE events, albeit with larger
OIR values, has been reported by @Vamvakas2020, fot the city of Patras.This site is
located $2.5^\circ$ closer to the equator.  south of Thessaloniki and is exposed to
air masses coming mainly from the eastern Mediterranean resulting in different cloud
patterns, that may affect the characteristics and magnitude of the CE events.

@@

We have identified `r ST_G0[, .N]` groups of CE in the
whole period of study, where the
group with the longest duration lasted
`r ST_G0[, max(GLB_diff.N)]` minutes on
`r strftime(ST_G0[which.max(GLB_diff.N), Date], "%d\\ %B %Y")`.
By examining the frequency distribution of the CEG durations
(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can conclude, that
although we detected some CEG with durations longer than an hour, about $80\,\%$ of
the CEG have a duration of less than 5 minutes.

```{r ceg-duration-distribution, echo=FALSE, fig.cap="Distribution of CE groups duration in minutes."}
knitr::include_graphics("../images/groups-1.png")
```

@@

```{r group-2d, echo=FALSE, fig.cap="Relation of the mean over irradiance and duration of GCE, where the color scale denotes the frequency of the respected events."}
knitr::include_graphics("../images/P-groups-bin2d-1.png")
```

>>>>

The distribution of the number of CE events as a function of OIR is shown in
Figure\nobreakspace{}\ref{fig:ovir-distribution}. Apparently, there is an inverse
relation between the frequency of CE events  and OIR with an exponential-like
decline. This is expected, as the stronger the CE events become, the rarer are the
conditions favoring the occurrence of CE events. For the majority (over $62\,\%$) of
the CE events the OIR is below the long term average of
$`r round(mean(ST_E_yearly$GLB_diff.mean), 1)`\,\text{W}/\text{m}^2$,
while about $8.1\,\%$ of the events correspond to OIR larger than
$100\,\text{W}/\text{m}^2$ and up to highest value of $412.4\,\text{W}/\text{m}^2$.
This distribution is indicative of the magnitude and the probability of the expected
CE events over Thessaloniki.  Similar distribution of CE events, albeit with larger
OIR values, has been reported by @Vamvakas2020, for the city of Patras.This site is
located $2.5^\circ$ south of Thessaloniki and is exposed to air masses coming mainly
from the eastern Mediterranean resulting in different cloud patterns, that may affect
the characteristics and magnitude of the CE events.

@@

We have identified `r ST_G0[, .N]` groups of CE in the
whole period of study, where the
group with the longest duration lasted
`r ST_G0[, max(GLB_diff.N)]` minutes on
`r strftime(ST_G0[which.max(GLB_diff.N), Date], "%d\\ %B %Y")`.

Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}) shows the frequency
distribution of the CE events according to their duration.  We conclude that although
some groups of events last for more than an hour about $80\,\%$ have duration of less
than 5 minutes.

```{r ceg-duration-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE groups of consequent CE events according to their duration."}
knitr::include_graphics("../images/groups-1.png")
```

@@

```{r group-2d, echo=FALSE, fig.cap="Relation of excess irradiation of CE groups with their duration. The logarithmic color scale denotes the frequency of the respective groups of events."}
knitr::include_graphics("../images/P-groups-bin2d-1.png")
```

### 2024-06-12 article/article.tex
Commit 2024-06-12 11:11

The distribution of the number of CE events as a function of OIR is
shown in Figure\nobreakspace{}\ref{fig:ovir-distribution}. Apparently,
there is an inverse relation between the frequency of CE events and OIR
with an exponential-like decline. This is expected, as the stronger the
CE events become, the rarer are the conditions favoring the occurrence
of CE events. For the majority (over \(62\%\)) of the CE events the OIR
is below the long term average of \(39.9\,\text{W}/\text{m}^2\), while
about \(8.1\%\) of the events correspond to OIR larger than
\(100\,\text{W}/\text{m}^2\) and up to highest value of
\(412.4\,\text{W}/\text{m}^2\). This distribution is indicative of the
magnitude and the probability of the expected CE events over
Thessaloniki. Similar distribution of CE events, albeit with larger OIR
values, has been reported by \citet{Vamvakas2020}, fot the city of
Patras.This site is located \(2.5^\circ\) closer to the equator. south
of Thessaloniki and is exposed to air masses coming mainly from the
eastern Mediterranean resulting in different cloud patterns, that may
affect the characteristics and magnitude of the CE events.

@@

We have identified 28468 groups of CE in the whole period of study,
where the group with the longest duration lasted 140 minutes on 07~July
2013. By examining the frequency distribution of the CEG durations
(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can
conclude, that although we detected some CEG with durations longer than
an hour, about \(80\,\%\) of the CEG have a duration of less than 5
minutes.

@@

\caption{Distribution of CE groups duration in minutes.}\label{fig:ceg-duration-distribution}
\end{figure}

@@

\caption{Relation of the mean over irradiance and duration of GCE, where the color scale denotes the frequency of the respected events.}\label{fig:group-2d}
\end{figure}

>>>>

The distribution of the number of CE events as a function of OIR is
shown in Figure\nobreakspace{}\ref{fig:ovir-distribution}. Apparently,
there is an inverse relation between the frequency of CE events and OIR
with an exponential-like decline. This is expected, as the stronger the
CE events become, the rarer are the conditions favoring the occurrence
of CE events. For the majority (over \(62\,\%\)) of the CE events the
OIR is below the long term average of \(39.9\,\text{W}/\text{m}^2\),
while about \(8.1\,\%\) of the events correspond to OIR larger than
\(100\,\text{W}/\text{m}^2\) and up to highest value of
\(412.4\,\text{W}/\text{m}^2\). This distribution is indicative of the
magnitude and the probability of the expected CE events over
Thessaloniki. Similar distribution of CE events, albeit with larger OIR
values, has been reported by \citet{Vamvakas2020}, for the city of
Patras.This site is located \(2.5^\circ\) south of Thessaloniki and is
exposed to air masses coming mainly from the eastern Mediterranean
resulting in different cloud patterns, that may affect the
characteristics and magnitude of the CE events.

@@

We have identified 28468 groups of CE in the whole period of study,
where the group with the longest duration lasted 140 minutes on 07~July
2013.

Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}) shows the
frequency distribution of the CE events according to their duration. We
conclude that although some groups of events last for more than an hour
about \(80\,\%\) have duration of less than 5 minutes.

@@

\caption{Relative frequency distribution of CE groups of consequent CE events according to their duration.}\label{fig:ceg-duration-distribution}
\end{figure}

@@

\caption{Relation of excess irradiation of CE groups with their duration. The logarithmic color scale denotes the frequency of the respective groups of events.}\label{fig:group-2d}
\end{figure}
